---
title: "You can't put a number to love, but researchers estimated one"
date: "2020-09-07"
categories: ["R"]
tags: ["R Blogdown, R Markdown", "ggplot2"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

Dating has drastically changed over the last decades. The modern world now provides new ways to find love, such as online matchmaking and speed dating. Although it's tough to put a number to love, have you ever wondered what are the odds of finding love?

Working with data scientists from eHarmony, an online dating website, experts from University of Bath  calculated that singletons have a **1 in 562 chance of finding love on any given day**, considering they leave it entirely to fate. This was based on 18 key factors, such as desired age, physical attractiveness, moral outlook or taste in music, which impact on the number of romantic options available to singles. 

Almost insignificant, right? To put that in perspective, there's a **1 in 55 chance of becoming a millionaire** if you're under 40, a **1 in 100 chance of being ambidextrous** and roughly a **1 in 400 trillion chance of you being born**. If it's a miracle that you exist today, finding love should be piece of cake, right?

Don't despair! Even though the odds may seem rather against your favor, they actually reveal that you can find your match after each 562 people you meet. They also have to like you back, don't they?

But the good news is that there are several things you can do to improve the odds and accelerate the chance of meeting your _The One_. Surprinsigly or not, all of them suggest you should get exposed to people as much as you can. 

##### Now that you know how use the odds in your favor, what are you waiting for?

```{r, tidy = FALSE, echo = FALSE, message = FALSE, warning = FALSE}
library(dplyr)
library(magrittr)
library(ggplot2)

# Label the odds in chart
label.odds <- c("Being set up by family members"
                ,"Meeting friends of friends"
                ,"Talking to people at clubs/bars"
                ,"Meeting people through shared hobbies/societies"
                ,"Talking to people at the gym"
                ,"Meeting colleagues and friends of colleagues"
                , "Meeting people via online dating site"
                ,"Fate only"
                )

# Standard fate odd
odds <- 1/562

# Increased odds by action undertaken
all.odds <- c(odds * 1.01
              , odds * 1.04
              , odds * 1.09
              , odds * 1.11
              , odds * 1.15
              , odds * 1.16
              , odds * 1.17
              , odds) %>%
  set_names( label.odds )

# Numeric labels for odds
label_num.odds <- c(paste0("+", 100 * round(all.odds[-8] - odds, digits = 5)), round(100 * odds, digits = 2)) %>% paste0("%")
x.val <- 1:length( all.odds )
data.df <- data.frame( as.factor(x.val), all.odds, label.odds ) %>%
  set_names( c("x", "odds", "label") )

# Create chart
ggplot(data = data.df, aes(x = x, y = odds, fill = x)) + 
  geom_bar(stat = "identity", show.legend = FALSE) +
  # scale_fill_viridis_d(direction = -1, alpha = 0.95, option = "D") +
  scale_fill_manual(values = viridis::viridis(9)[-9] %>% rev(), aesthetics = "fill") + 
  coord_flip() +
  ggtitle("Daily actions to increase your odds of finding love") + 
  geom_text( aes( label = label.odds ), colour = "white", hjust = 1.1, fontface = "bold") + 
  geom_text( aes ( label = label_num.odds ), hjust = -0.1, fontface = "bold") +
  theme_void() +
  scale_y_continuous(name = "Odds of finding love in 365 days", limits = c(0, 0.0023)) +
  theme(plot.title = element_text(hjust = 0.4, face = "bold"))
```

Sources: [Daily Mail, 2017](https://www.dailymail.co.uk/sciencetech/article-4757816/Mathematicians-reveal-odds-finding-love.html); [eHarmony, 2017](https://www.eharmony.co.uk/dating-advice/dating/odds-of-love); [Bloomberg, 2016](https://www.bloomberg.com/features/2016-millionaire-odds/); [Reader's Digest, 2019](https://www.rd.com/list/facts-ambidextrous-people/); [Business Insider, 2012](https://www.businessinsider.com/infographic-the-odds-of-being-alive-2012-6).